Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
Defining predicate system over Set.

@@

Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over $\Set$,
$\cat{C}$ a category and $F: \cat{C}^\op \to \Set$ a presheaf. Define a \emph{predicate on $F$} to be a family
of predicates $P_X \in \Pred_\mathcal{S}(F(X))$ for every object $X$ in $\cat{C}$ such that $P_Y \sqsubseteq
\reindex{P_X}{F(f)}$ for every $f: X \to Y$ in $\cat{C}$.

>>>>

\subsubsection{Predicate system over $\Set$}

Suppose $X$ a set. Define a \emph{predicate on $X$} to be a family of (proof-irrelevant) propositions. For any
function $f: X \to Y$, define $\reindex{P}{f}(x)$ iff $P(f(x))$ and $\directImage{P}{f}(y)$ iff there exists
$x = f(y)$ such that $P(x)$. Define $\mathcal{S}$ to be the predicate system over $\Set$ which assigns to any
set $X$ the set $\Pred(X)$ of propositions on $X$ ordered by implication, with $\top, \meet, \join$ and
$\residual$ defined pointwise.

@@

Suppose $\cat{C}$ a category and $F: \cat{C}^\op \to \Set$ a presheaf. Define a \emph{predicate on $F$} to be
a family of predicates $P_X \in \Pred_\mathcal{S}(F(X))$ for every object $X$ in $\cat{C}$ such that $P_Y
\sqsubseteq \reindex{P_X}{F(f)}$ for every $f: X \to Y$ in $\cat{C}$.
